%%% A template to produce a nice-looking Curriculum Vitae.
%%% Kieran Healy <kjhealy@gmail.com>
%%% Most recent version is at http://kjhealy.github.com/kjh-vita
%%%
%%% ------------------------------------------------------------------------
%%% Requirements that are included in a modern tex distribution:
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%% memoir.cls
%%% fontawesome.sty
%%%
%%% 
%%% 
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}   
\usepackage{org-preamble-xelatex} 
\usepackage{fontawesome,url}


%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{John C. Flournoy}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{Harvard University}
\def\myaddress{Department of Psychology}
\def\myemail{john\_flournoy@fas.harvard.edu}
\def\myweb{jflournoy.github.io}
\def\myorcid{orcid.org/0000-0003-1735-1221}
\def\mygithub{github.com/jflournoy}
\def\myphone{(415) 260-2744}
\def\myfax{}
\def\mytwitter{@flourneuro}
\def\myversion{}
\def\myrevision{}

\def\myaffiliation{University of Oregon}
\def\myauthor{John C. Flournoy}
\date{\today} % not used (revision control instead)
\def\mykeywords{Flournoy, John Flournoy, Vita, CV, Resume, Psychology, Neuroscience}

%%%------------------------------------------------------------------------  
%%% Git version tracking 
%%%------------------------------------------------------------------------

%% If you don't use git or the vc package (from CTAN), comment this out.
%% If you comment it out, be sure to remove the \rfoot comment below, too.
% \input{vc}

%% uncomment if you want to use biblatex
% \usepackage{enable-biblatex}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.

%% Use Caladea instead, which is already available on the server
\setromanfont[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]%{Minion Pro}
    {Caladea}
    
%% Use Cabin instead, which is already available on the server
\setsansfont[Mapping=tex-text,
	Ligatures={Common}, 
	Colour=AA0000]%{Unit-Medium}
    {Cabin}

%% Use Fira Mono instead, which is already available on the server
\setmonofont[Mapping=tex-text,Scale=0.85]%{PragmataPro} 
{Fira Mono}

% \newfontface\scheader[SmallCapsFont={Minion Pro},SmallCapsFeatures={Letters=SmallCaps}]{Minion Pro}
%% Caladea doesn't have small caps, so don't use this.
\let\scheader\relax

% \newfontface\addressblock[Mapping={tex-text}, 
% 	Numbers={OldStyle},
% 	Ligatures={Common}]{Minion Pro Medium Caption}
\newfontface\addressblock[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Caladea}


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
% \newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the vc
% package---see docs for vc package for details. Comment out this line
% if you're not using vc, and also remove the \input{vc} line above.
\pagestyle{kjh}
\thispagestyle{kjhgit}


%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize 
 \href{https://psychology.fas.harvard.edu/}{Department of Psychology} \\ William James Hall \\ 33 Kirkland Street \\ \vspace{-0.05in}Cambridge, \textsc{MA} 02138}  
  
\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.8in}
  \flushright \footnotesize  \addressblock \myphone \, \faPhone  \\ 
  {\scriptsize  \texttt{\href{mailto:\myemail}{email}} \, \faEnvelope} \\
  {\scriptsize  \texttt{\href{http://\myweb}{\myweb}} \, \faGlobe} \\
  {\scriptsize  \texttt{\href{http://\mygithub}{\mygithub}} \, \faGithub} \\ 
  {\scriptsize  \texttt{\href{http://twitter.com/flourneuro}{\mytwitter}} \, \faTwitter }
\end{minipage}

\medskip

%% Name 
% \noindent{\LARGE\scheader \textsc{john c flournoy}}
\noindent{\Large\bfseries John C Flournoy}\newline\noindent{Postdoctoral Fellow}\newline\noindent{\today}
\reversemarginpar

\bigskip       


%% Work
% \medskip
\marginhead{\sffamily {\vskip -0.4em} positions}

\ind Postdoctoral Fellow, Harvard University, 2018--present

\ind Graduate Research/Teaching Fellow, University of Oregon, 2012--2018

\ind Research Coordinator, Stanford University School of Medicine, 2009--2012

\bigskip

%% Education

\marginhead{\sffamily {{\vskip -0.23em} education}}

\ind Ph.D. Psychology, University of Oregon, 2018

\ind M.S. Psychology, University of Oregon, 2014

\ind B.A. Cognitive Science, University of California, Berkeley, 2004

\bigskip
 
%% Publications
\marginhead{\sffamily {\vskip 0.35em} journal articles}
\medskip
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\ind Ludwig, R. M., \textbf{Flournoy, J. C.}, \& Berkman, E. T. (registration accepted). Inequality in personality and temporal discounting across socioeconomic status? Assessing the evidence. \textit{Journal of Research in Personality}.

\ind Thalmayer, A. G., Saucier, G., \textbf{Flournoy, J. C.},  \&  Srivastava, S. (under review). Ethics-Relevant Values as Antecedents of Personality Change:
Longitudinal Findings from the Life and Time Study.

\ind Thalmayer, A. G., Saucier, G., Srivastava, S.,  \textbf{Flournoy, J. C.} \& Costello, C. C. (revision submitted). Ethics-Relevant Values in Adulthood: Longitudinal Findings from the Life and Time Study.

\ind de Macks, Z. A. O., Flannery, J. E., Peake, S. J., \textbf{Flournoy, J. C.}, Mobasser, A., Alberti, S. L., ... \& Pfeifer, J. H. (2018). Novel insights from the Yellow Light Game: Safe and risky decisions differentially impact adolescent outcome-related brain function. \textit{NeuroImage}. \href{https://doi.org/10.1016/j.neuroimage.2018.06.058}{10.1016/j.neuroimage.2018.06.058}

\ind Flannery, J. E., Giuliani, N., \textbf{Flournoy, J. C.}, \& Pfeifer, J. H. (2017). Neurodevelopmental Changes Across Adolescence in Viewing and Labeling Dynamic Peer Emotions. \textit{Developmental Cognitive Neuroscience}. \newline\href{http://dx.doi.org/10.1016/j.dcn.2017.02.003}{10.1016/j.dcn.2017.02.003}

\ind Giuliani, N. R., \textbf{Flournoy, J. C.}, Ivie, E. J., Von Hippel, A., \& Pfeifer, J. H. (2017). Presentation and Validation of the DuckEES Child and Adolescent Dynamic Facial Expressions Stimulus Set. \textit{International Journal of Methods in Psychiatric Research}. \href{https://doi.org/10.1002/mpr.1553}{10.1002/mpr.1553}

\ind King, K. M., Littlefield, A., McCabe, C., Mills, K. L., \textbf{Flournoy, J. C.}, \& Chassin, L. (2017). Longitudinal modeling in developmental neuroimaging research: Common challenges, and solutions from developmental psychology. \textit{Developmental Cognitive Neuroscience}. \href{https://doi.org/10.1016/j.dcn.2017.11.009}{10.1016/j.dcn.2017.11.009}

\ind Leonard, J. A.\footnote{Authors contributed equally}, \textbf{Flournoy, J. C.}\footnotemark[1], Lewis-de los Angeles, C. P. \& Whitaker, K. J. (2017). How much motion is too much motion? Determining motion thresholds by sample size for reproducibility in developmental resting-state MRI. \textit{Research Ideas and Outcomes} 3: e12569. \href{https://doi.org/10.3897/rio.3.e12569}{10.3897/rio.3.e12569}

\ind Madhyastha, T., Peverill, M., Koh, N., McCabe, C., \textbf{Flournoy, J. C.}, Mills, K. L., King, K. M., Pfeifer, J. H., \& McLaughlin, K. A. (2017). Current methods and limitations for longitudinal fMRI analysis across development. \textit{Developmental Cognitive Neuroscience}. \href{https://doi.org/10.1016/j.dcn.2017.11.006}{10.1016/j.dcn.2017.11.006}

\ind Matta, T., \textbf{Flournoy, J. C.}, \& Byrne, M. (2017). Making an unknown unknown a known unknown: Missing data in longitudinal neuroimaging studies. \textit{Developmental Cognitive Neuroscience}. \href{https://doi.org/10.1016/j.dcn.2017.10.001}{10.1016/j.dcn.2017.10.001}.\newline PsyArXiv:\href{https://dx.doi.org/10.31234/osf.io/6hfxc}{10.31234/osf.io/6hfxc}

\ind \textbf{Flournoy, J. C.}, Pfeifer, J. H., Moore, W. E., Tackman, A. M., Masten, C. L., Mazziotta, J. C., ... Dapretto, M. (2016). Neural Reactivity to Emotional Faces May Mediate the Relationship Between Childhood Empathy and Adolescent Prosocial Behavior. \textit{Child Development}, 87(6), 1691–1702. \newline\href{https://doi.org/10.1111/cdev.12630}{10.1111/cdev.12630}

\ind Goodkind, M. S., Gallagher-Thompson, D., Thompson, L. W., Kesler, S. R., Anker, L., \textbf{Flournoy, J.}, ... O’Hara, R. M. (2015). The impact of executive function on response to cognitive behavioral therapy in late-life depression. \textit{International Journal of Geriatric Psychiatry}. \href{http://doi.org/10.1002/gps.4325}{10.1002/gps.4325}

\ind O’Hara, R., Marcus, P., Thompson, W. K., \textbf{Flournoy, J.}, Vahia, I., Lin, X., ... Jeste, D. V. (2012). 5-HTTLPR Short Allele, Resilience, and Successful Aging in Older Adults. \textit{American Journal of Geriatric Psych}. \newline\href{http://doi.org/10.1097/JGP.0b013e31823e2d03}{10.1097/JGP.0b013e31823e2d03}


%% Use revnumerate environment if numbered publications are needed. 
%% (Include it above in the preamble).
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}
\bigskip
\marginhead{\sffamily {\vskip 0.35em} Talks}
\medskip

\ind (\textit{co-presenter}) Cosme, D. E., \textbf{Flournoy, J. C.}, Telzer, E., \& Pfeifer, J. H.  (2017, September). Traditional Modeling Approaches. Presented at the \href{https://osf.io/hym23/}{Modeling Developmental Change workshop}, Portland, OR.

\ind (\textit{co-presenter}) \textbf{Flournoy, J. C.}, Cosme, D. E., \& Pfeifer, J. H. (2017, September). Orientation to fMRI. Presented at the \href{https://osf.io/hym23/}{Modeling Developmental Change workshop}, Portland, OR.

\ind (\textit{co-presenter}) Pfeifer, J. H., \& \textbf{Flournoy, J. C.} (2016, April). Characterizing longitudinal change in brain function: Some problems and solutions. Presented at the Modeling Developmental Change conference, Eugene, OR.

\ind (\textit{contributor}) Srivastava, S., \textbf{Flournoy, J. C.}, Lawless DesJardins, N., \& Saucier, G. (2015, June). Effects of Work Roles and Investments on Personality Change in Adulthood: Findings from a 4-year Accelerated Longitudinal Study. Presented at the 4th biennial meeting of the Association for Research in Personality, St. Louis, MO.

\ind (\textit{contributor}) Tackman, A. M., Srivastava, S., \textbf{Flournoy, J. C.}, \& Saucier, G. (2015, February). Relationships and personality development in adulthood: A multiple-informant approach. Presented at the 16th annual meeting of the Society of Personality and Social Psychology, Long Beach, CA.

\ind (\textit{presenter}) \textbf{Flournoy, J. C.}, Moore III, W. E., \& Pfeifer, J. H. (2014, September). Using fMRI to study child and adolescent development: Thoughts from the trenches. Presented at the Special Meeting of the Society for Research in Child Development on Developmental Methodology, San Diego, CA.

%% Publications
\bigskip
\marginhead{\sffamily {\vskip 0.5em} Posters}
\medskip

\ind Flannery, J., Peake, S. J., \textbf{Flournoy, J. C.}, Alberti, S. L., Mobasser, A., Fisher, P. A., \& Pfeifer, J. H. (2016). Neural Outcomes of Risk Decision: Prediction of Subsequent Behavioral Decision Across Social Contexts in Adolescence. Presented at the Annual Social Affective Neuroscience Conference, New York, NY.

\ind Flannery, J. E., Giuliani, N., \textbf{Flournoy, J. C.}, \& Pfeifer, J. H. (2015). Developmental Changes in Affect Processing: Brain Functionand Connectivityto Peer Faces. Presented at the 8th Annual Meeting of the Social Affective Neuroscience Society Annual Meeting, Boston, MA.

\ind Flannery, J., Giuliani, N., \textbf{Flournoy, J. C.}, \& Pfeifer, J. H. (2015). Affective Reactivity and Regulation Across Adolescence: Neural Responses to Dynamic Peer Emotions. Presented at the Social Affective Neuroscience Society Annual Meeting, Boston, MA.

\ind Flannery, J., Peake, S. J., \textbf{Flournoy, J. C.}, Alberti, S. L., Mobasser, A., Fisher, P. A., \& Pfeifer, J. H. (2015). Positive and Negative Neural Feedback Processing of Risk Decisions Across Social Contexts in Adolescents. Presented at the 3rd Annual Flux Congress, Leiden, Netherlands.

\ind \textbf{Flournoy, J. C.}, Peake, S. J., Alberti, S. L., Flannery, J. E., Mobasser, A., Fisher, P. A., \& Pfeifer, J. H. (2015). Evaluation of a Bayesian cognitive model for adolescent risky decision making in the Stoplight Game. Presented at the Flux Congress, Leiden, Netherlands. \href{https://doi.org/10.6084/m9.figshare.5393329.v1}{10.6084/m9.figshare.5393329.v1}

\ind \textbf{Flournoy, J. C.}, Srivastava, S., \& Saucier, G. (2015). A Network Approach to Longitudinal Personality Change. Presented at the Association for Research in Personality, 4th Biennial Meeting, St. Louis, MO. \newline\href{https://doi.org/10.6084/m9.figshare.1447279.v2}{10.6084/m9.figshare.1447279.v2}

\ind Flannery, J., Giuliani, N., \textbf{Flournoy, J. C.}, \& Pfeifer, J. H. (2014). Dynamic Neuropsychological Emotion Regulation Profiles Among Youth, 10-22 Year Old. Presented at the International Society of Developmental Psychobiology, Washington, D.C.

\ind \textbf{Flournoy, J. C.}, Giuliani, N., Hill, A., Moore III, W. E., \& Pfeifer, J. H. (2014). Labeling Emotional Faces Changes Affective Processing. Presented at the The Society for Research on Adolescence 15th Biennial Meeting, Austin, TX.

\ind \textbf{Flournoy, J. C.}, Srivastava, S., Dapretto, M., \& Pfeifer, J. H. (2014). Correlated Change in Components of Empathy During Adolescence. Presented at the The Society for Personality and Social Psychology 15th Annual Meeting, Austin, TX.

\ind \textbf{Flournoy, J. C.}, Tackman, A., Moore III, W. E., Pfeifer, J. H., Mazziotta, J. C., Iacoboni, M., \& Dapretto, M. (2014). Effect of Empathy on Prosocial Behavior Mediated by Brain Across the Transition into Adolescence. Presented at the Social \& Affective Neuroscience Society 7th Annual Meeting, Denver, CO.

\ind \textbf{Flournoy, J. C.}, Moore III, W. E., Srivastava, S., Mazziotta, J. C., Iacoboni, M., Dapretto, M., \& Pfeifer, J. H. (2013). Neural Correlates of Empathy Development During Early Adolescence. Presented at the Social \& Affective Neuroscience Society 6th Annual Meeting, San Francisco, CA.

\ind Chen, E., Anker, L., \textbf{Flournoy, J.}, Kovachy, B., Blaisdell, K., Weinkam, T., … O’Hara, R. (2011). Comparison of Amount of REM Sleep and Cognitive Abilities in Normal Older Adults and Those with Sleep Apnea. Presented at the International College Of Geriatric Psychoneuropharmacology 11th Annual Meeting.

\ind \textbf{Flournoy, J.}, Weinkam, T., Hallmayer, J., \& O’Hara, R. (2011). Anxiety, Sleep Efficiency, and 5-HTTLPR Genotype in Older Adults. Presented at the Cognitive Neuroscience Society 18th Annual Meeting, San Francisco, CA.

\ind Marcus, P., Thompson, W. K., \textbf{Flournoy, J.}, Vahia, I., Lin, X., Hallmayer, J., … O’Hara, R. (2010). 5-HTTLPR Short allele is Associated with Poorer Self-Perceptions of Successful Aging in Older Adults. Presented at the International College Of Geriatric Psychoneuropharmacology 10th Annual Meeting, Athens, Greece.

\marginhead{\sffamily {\vskip 0.6em} Chapters}
\medskip

\ind Sudheimer, K., \textbf{Flournoy, J.}, Gershon, A., Demuth, B., Schatzberg, A., \& O’Hara, R. (2013). The HPA Axis and Late Life Depression. In H. Lavretsky, M. Sajatovic, \& C. Reynolds (Eds.), Late-Life Mood Disorders (1st ed.). Oxford University Press, USA.


\bigskip
\marginhead{\sffamily {\vskip 0.3em}Awards}
\medskip

\ind Gary E. Smith Summer Professional Development Award, 2015

\ind Clarence and Lucille Dunbar Scholarship , 2014

\marginhead{\sffamily {\vskip 0.6em}Special training}
\medskip

\ind \textit{ICPSR Summer Program in Quantitative Methods of Social Research, 2015}\newline 
Causal Inference for the Social Sciences\newline
Advanced Bayesian Models for the Social Sciences



\marginhead{\sffamily {\vskip 0.6em}Service}
\medskip

\ind \textit{Co-organizer}: \newline Brainhack Global 2017 @ Eugene, OR

\ind \textit{Facilitator}: \newline UO Data Science Club, 2013--2017

\ind \textit{Reviewer}:\newline 
Developmental Cognitive Neuroscience

\ind \textit{Co-reviewer}: \newline Developmental Cognitive Neuroscience\newline Society for Research in Child Development, Biennial Meeting, 2017\newline Journal of the American Academy of Child and Adolescent Psychiatry \newline Developmental Neuroscience

\ind \textit{Member}: \newline Graduate Admissions Committees, Psychology, University of Oregon, 2014

\ind \textit{Coordinator}: \newline Developmental Psychology Brown Bag, University of Oregon, Winter 2013

\bigskip
\marginhead{\sffamily {\vskip 0.3em}Professional Memberships}
\medskip
\ind Member, Society for the Improvement of Psychological Science, 2018-2020

\end{document}
